PhD Title \\ PhD Thesis

### 2024-07-11 Latex_files/Thesis/chapters/chapter 4/main.tex
updates

In this chapter we consider how the addition of a second sphere into an optical trap can radically effect its dynamics, to the extent that one can no longer rely on typical calibration techniques to characterise the interactions.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Positional and Orientational dependence of Trapping forces}

@@

\begin{figure}[h!]
	\centering
	\begin{subfigure}{.475\linewidth}
		\includegraphics[width=\linewidth]{lam=2_theta=0.png}
		\caption{}
		\label{lam=2}
	\end{subfigure}\hfill % <-- "\hfill"
	\begin{subfigure}{.475\linewidth}
		\includegraphics[width=\linewidth]{lam=2_theta=180.png}
		\caption{}
		\label{lam=2_inverted}
	\end{subfigure}\hfill % <-- "\hfill"
	\medskip
	\begin{subfigure}{.475\linewidth}
		\centering
		\raisebox{-45pt}[0pt][0pt]{\makebox{}\includegraphics[width=0.3\linewidth, keepaspectratio]{theta=0.png}}
		\label{large over small}
	\end{subfigure}
	\begin{subfigure}{.475\linewidth}
		\centering
		\includegraphics[width=0.3\linewidth,
		keepaspectratio]{theta=180.png}
		\label{small_over_large}
	\end{subfigure}
	\caption{Plots of force vs displacement of the point of the contact of the spheres (µm) for the case of a dimer of size ratio 2. (a) is the case where the smaller sphere is orientated with the beam propagation direction. (b) is the inverted case, smaller sphere oriented against the propagation direction. Renders to visualise the dimer orientation are shown below each plot The black lines on each force-curve is a linear fit with the slope being reported as the trap stiffness in the legend.}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\begin{subfigure}{0.85\linewidth}
		\includegraphics[width=\linewidth]{Equillibrium_positions.png}
		\caption{}
		\label{eq_pos}
	\end{subfigure}\hfill % <-- "\hfill"
	\medskip
	\begin{subfigure}{0.85\linewidth}
		\includegraphics[width=\linewidth]{Equillibrium_positions_inverted.png}
		\caption{}
		\label{eq_pos_inverted}
	\end{subfigure}
	\caption{Equilibrium positions of optically trapped dimers with varying size ratio, dotted lines represent unstable traps whereas solid lines represent stable trapping positions. (a) shows that dimers with their smaller sphere orientated away from the focus have an expected single trapping position. (b) shows that when the same dimer is inverted $180^\circ$ there are now stable traps along the beam axis, one below the focus and one above the focus.}
\end{figure}
\newpage
\subsection{Non-trivial harmonic traps}\label{sec:off-axis}
Computing the equilibrium positions when a dimer is aligned with the electric field is relatively simple as the orientational torque is minimised (see Eq.\ref{eq:opt_torque}), meaning once trapped the dimer is unlikely to change orientation enough to escape the trap. However, that does not rule out the possibility that there is a stable orientation that is not strictly vertical, in fact most experimental work with symmetric dimers will trap them lying perpendicular to the beam direction \cite{Ahn2018}. Unlike before where we can simply find the trap by varying the dimer's vertical position its instead more prudent to run a multitude of smaller simulations at a variety of starting positions and orientations. An example for a dimer of size ratio 2 is shown below:
\begin{figure}[h!]
	\centering
	\begin{subfigure}{0.67\linewidth}
		\includegraphics[width=\linewidth]{off_axis_trap.png}
	\end{subfigure}
	\begin{subfigure}{0.32\linewidth}
		\raisebox{-110pt}[0pt][0pt]{\makebox{}\includegraphics[width=\linewidth, keepaspectratio]{off_axis_render.png}}
		\caption{}
	\end{subfigure}
	\captionsetup{hangindent=2.35cm}
	\caption{Trajectory map of simulations ran using a dimer of size ratio 2 with a laser power of 500 mW. The stable points are indicated by the larger spheres and the starting conditions are colour coded to match the stable point they end up in. Right hand render shows a dimer in its off-axis configuration}
\end{figure}

@@

One aspect that has yet to be covered in depth with regards to
spherical aggregates of any construction is their interaction with
circularly polarised light. Typically the spin density of an electric
field cannot be reduced in homogenous medium due to the fact that the
spin angular momentum is conserved locally. In which case the only way
to transfer angular momentum to use an object that is anisotropic.
This is seen most clearly with birefringent materials, due to fact that
the crystal lattice itself is anisotropic, a circularly polarised beam
will transfer an optical torque that is proportional to the difference in 
the refractive index of the particle. The optical torque is given as:
\begin{equation}
	\label{eq:opt_torque}
	\begin{aligned}
		\tau_{opt} = \frac{\epsilon}{2\omega_{laser}}E_0^2 (1-cos(kd(\Delta n))sin2\phi)
	\end{aligned}
\end{equation}
Where $\Delta n$ is the difference in refractive indices of the 
particle, and $\phi$ indicates the phase shift in the electric field
(for circular polarised light $\phi= \pi/4$) However, theoretical and
experimental work by \cite{Yevick2017} found that highly focused
Gaussian beams could produce second order effects in the Rayleigh
regime resulting in a photo-kinetic force that results in orbital
motion about the beam's central axis. This effect is rather minimal
for single sphere's, resulting in a orbital frequency on the order of
$10^{-1}\,{\rm Hz}$, with an order of magnitude difference when
trapping aggregates of spheres.  They computed the circulation rate by
computing the time-average probability flux; however, when extended to
the Mie regime we see a completely different behaviour, instead
experiencing an optical torque about their long axis.S This rotation
was first noted by Vigilante and co-workers who only considered this
behaviour for a symmetric dimer \cite{Vigilante2020}; we run number of
simulations for differently sized dimers in a circularly polarised
trap and looked at the rotation rate.  We found that not only is the
rotation rate dependent on the size of the dimer, but also on its
orientation and therefore their axial position.

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{rotation_rate_vs_size.png}
  \caption{Rotation rate plotted against dimer size ratio for a variety of different simulation scenarios. The red line is for the case where the larger sphere is above the smaller sphere. The blue line is the inverted case, while the initial position is above the focus of the trap. And lastly the green line is again for the inverted case, but when the dimer's initial position is below the focus of the trap.}
\end{figure}

It is difficult to see from the graph, but the rotation rate never
truly goes down to zero, reaching a minimum of $2\,{\rm Hz}$, which would
imply that a second sphere of radius $200\,{\rm nm}$ is enough to
induce rotational motion.  We used MSTM to look at the stokes
parameters from the scattered field from a simple plane wave incident
on our dimer, the proportion of circularly polarised light is minimal
compared to the proportion of plane polarised light, which indicates
that this rotational motion is not due to any inhomogeneity in the
dimer that might impart angular momentum to the scattered beam - as
compared to a anisotropic scatterer like Vaterite.

These results are somewhat contrary to other work with silica dimers
\cite{Ahn2018, Debuysschere2023,Reimann2018}; previous experiments
have trapped the dimer in an orientation perpendicular to the beam
propagation direction.  The rotational motion is induced due to the
asymmetric geometry creating an unbalanced polarisation susceptibility
along its long axis as compared to its short axis; therefore its long
axis is aligned with the polarisation vector and can rotate
freely\cite{Ahn2018}.  This however cannot be the case with our
simulations as the dimer rotates about its long axis, meaning there
cannot be an asymmetric axis to align with the beam's polarisation
vector. Furthermore, we see a non-linear increase in the rotational
speed of our dimers with size, the drag torque from the surrounding
fluid is $\propto r^3$ so the expectation is that the rotation
frequency should fall off with increasing size.  This indicates that
the rotational motion is due to the shape asymmetry of the dimer and
not solely due to the beam's angular momentum.  Measurement of this
photo-kinetic force is difficult to achieve due to the fact that
previous analysis was conducted in the Rayleigh regime, where the
polarizability of our dimer can be approximated as:
\begin{align}
  \bold{p}({\bf r},t)
  =
  \alpha_x E_x({\bf r},t)\hat{\bf e}_x
  + \alpha_yE_y({\bf r},t)\hat{\bf e}_y
  + \alpha_zE_z({\bf r},t)\hat{\bf e}_z
\end{align}
where the polarizability is given as a 3D vector for the three
principle Cartesian directions.  In order to measure the magnitude of
second order contributions we would need to construct a dipole array
that fully captures the scattering of a dimer. Measuring the optical torque 
makes it clear that the polarizability is a contributing factor to this optical 
rotation phenomena. Rotating a symmetric dimer in the $x-z$ plane reveals 
that while the dimer can be rotated in an orientation perpendicular 
to the beam rotational torque is maximised when rotated while aligned with 
the optical axis.
\begin{SCfigure}
	\includegraphics[width=0.65\linewidth,height= 15cm]{torque_different_polarisations.png}
	\caption{Optical torque against polar angle $\theta$ about the three primary axis (top: torque about the x-axis; middle: torque about the y-axis; bottom: torque about the z-axis) on a symmetric dimer in linear, elliptical, and circular polarisation beams. Diagram to the right is for visual clarity about the direction of $\theta$.\vspace{4.5cm}}
\end{SCfigure}
\newpage

@@

As a benchmark we start by considering a single sphere within 
an optical trap. After a 3 second trajectory (the typical time
necessary to collect a power spectrum) the sphere's power 
spectra was recorded and a fitted to eq.~\ref{eq:alaised_lorentzian}.
\begin{figure}[h]
	\label{fig:psd_sphere}
	\centering
	\includegraphics[width=\linewidth]{PSD_sphere.png}
	\caption{Recorded power spectra fitted to eq.~\ref{eq:alaised_lorentzian}, scattered points represents
	the blocked data ($n_b=100$). Corner frequency for the 
	Lorentzians are reported in the legend.}
\end{figure}

@@

Where the ellipticity of the beam is given by 
$e = (1-\kappa_y/\kappa_x)^{0.5}$ and is a measure of the symmetry of 
the beam wavefront. Its clear from these initial results that the 
QPD is more sensitive to changes along the y-axis than the x-axis 
when compared to the direct \textit{ott} calculations. Typically,
even an industrial Gaussian beam will produce an elliptical diffraction
limit spot when heavily focused; in their tutorial for optimizing 
the PSD analysis, Berg and Sorensen reported a ellipticity of
around 15 \% after a total calibration time of 81 seconds 
\cite{BergSoerensen2004}. The reason for this discrepancy
can be explained partly by the fact that our estimation of the 
trap geometry via \textit{ott} is based on the the actual 
interactions with the beam near close to the focus whereas
a QPD is estimating the trap geometry by extrapolating from
far field scattering signals. If we now consider a symmetric the 
discrepancy between \textit{ott} and the simulated QPD grows.

@@

Now we see that the \textit{ott} predicts a more elliptical 
trap compared to the QPD model which says the trap is far
more symmetrical while trapping a symmetric dimer. The reason that
\textit{ott} no longer expects a circular trap could be due to
how it computes the beam shape coefficients; by point matching in 
the far field before the focus means a loss in accuracy for objects
that trap above the focus. The change in the QPD estimation  
can be partially explained by the fact that rotational
effects are not accounted for in the Lorentzian power spectra,
only translational motion. Typically, rotational motion is only
ever detected when it is periodic (take for example a power spectra
from a rotating birefringent sphere), when the motion is stochastic
the entire power spectra is effected making it near impossible
to separate the translational and rotational contributions from a 
single power spectra.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
\comment{Conclusions still need to be written out}

>>>>

In this chapter we consider how the addition of a second sphere into an optical trap can radically effect its dynamics, to the extent that one can no longer rely on typical calibration techniques to characterise the interactions.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Positional and Orientational dependence of Trapping forces}

@@

\begin{figure}[h!]
	\centering
	\begin{subfigure}{.475\linewidth}
		\includegraphics[width=\linewidth]{lam=2_theta=0.png}
		\caption{}
		\label{lam=2}
	\end{subfigure}\hfill % <-- "\hfill"
	\begin{subfigure}{.475\linewidth}
		\includegraphics[width=\linewidth]{lam=2_theta=180.png}
		\caption{}
		\label{lam=2_inverted}
	\end{subfigure}\hfill % <-- "\hfill"
	\medskip
	\begin{subfigure}{.475\linewidth}
		\centering
		\raisebox{60pt}[0pt][0pt]{\makebox{}\includegraphics[width=0.3\linewidth, keepaspectratio]{theta=0.png}}
		\label{large over small}
	\end{subfigure}
	\begin{subfigure}{.475\linewidth}
		\centering
		\includegraphics[width=0.3\linewidth,
		keepaspectratio]{theta=180.png}
		\label{small_over_large}
	\end{subfigure}
	\caption{Plots of force vs displacement of the point of the contact of the spheres (µm) for the case of a dimer of size ratio 2. (a) is the case where the smaller sphere is orientated with the beam propagation direction. (b) is the inverted case, smaller sphere oriented against the propagation direction. Renders to visualise the dimer orientation are shown below each plot The black lines on each force-curve is a linear fit with the slope being reported as the trap stiffness in the legend.}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\begin{subfigure}{0.85\linewidth}
		\includegraphics[width=\linewidth]{Equillibrium_positions.png}
		\caption{}
		\label{eq_pos}
	\end{subfigure}\hfill % <-- "\hfill"
	\medskip
	\begin{subfigure}{0.85\linewidth}
		\includegraphics[width=\linewidth]{Equillibrium_positions_inverted.png}
		\caption{}
		\label{eq_pos_inverted}
	\end{subfigure}
	\caption{Equilibrium positions of optically trapped dimers with varying size ratio, dotted lines represent unstable traps whereas solid lines represent stable trapping positions. (a) shows that dimers with their smaller sphere orientated away from the focus have an expected single trapping position. (b) shows that when the same dimer is inverted $180^\circ$ there are now stable traps along the beam axis, one below the focus and one above the focus.}
\end{figure}

\subsection{Non-trivial harmonic traps}
\label{sec:off-axis}
Computing the equilibrium positions when a dimer is aligned with the electric field is relatively simple as the orientational torque is minimised (see Eq.\ref{eq:opt_torque}), meaning once trapped the dimer is unlikely to change orientation enough to escape the trap. However, that does not rule out the possibility that there is a stable orientation that is not strictly vertical, in fact most experimental work with symmetric dimers will trap them lying perpendicular to the beam direction \cite{Ahn2018}. Unlike before where we can simply find the trap by varying the dimer's vertical position its instead more prudent to run a multitude of smaller simulations at a variety of starting positions and orientations. An example for a dimer of size ratio 2 is shown below:
\begin{figure}[h!]
	\centering
	\begin{subfigure}{0.67\linewidth}
		\includegraphics[width=\linewidth]{off_axis_trap.png}
	\end{subfigure}
	\begin{subfigure}{0.32\linewidth}
		\raisebox{0pt}[0pt][0pt]{\makebox{}\includegraphics[width=\linewidth, keepaspectratio]{off_axis_render.png}}
		\caption{}
	\end{subfigure}
	\captionsetup{hangindent=2.35cm}
	\caption{Trajectory map of simulations ran using a dimer of size ratio 2 with a laser power of 500 mW. The stable points are indicated by the larger spheres and the starting conditions are colour coded to match the stable point they end up in. Right hand render shows a dimer in its off-axis configuration}
\end{figure}

@@

One aspect that has yet to be covered in depth with regards to
spherical aggregates of any construction is their interaction with
circularly polarised light. While most homogenous objects are trapped
no differently in different polarisations, dimers have been shown to
experience an optical torque \cite{Vigilante2020, Ahn2018, Reimann2018}. 
Typically the spin density of an electric field cannot be reduced in 
homogenous medium due to the fact that the spin angular momentum is 
conserved locally. In which case the only way to transfer angular 
momentum to use an object that is anisotropic. This is seen most 
clearly with birefringent materials, due to fact that the crystal 
lattice itself is anisotropic, a circularly polarised beam will 
transfer an optical torque that is proportional to the difference in 
the refractive index of the particle. The optical torque is given as:
\begin{equation}
	\label{eq:opt_torque}
	\begin{aligned}
		\tau_{opt} = \frac{\epsilon}{2\omega_{laser}}E_0^2 (1-cos(kd(\Delta n))sin2\phi)
	\end{aligned}
\end{equation}

Where $\Delta n$ is the difference in refractive indices of the 
particle, and $\phi$ indicates the phase shift in the electric field
(for circular polarised light $\phi= \pi/4$). The optical rotation seen
with dimers can be attributed to the polarisation of the trapping beam as
taking a Fourier transform of the transverse components of the dimers 
orientation time series reveals a clean rotation rate. 
\begin{figure}[h!]
	\centering
	\includegraphics[width=0.9\linewidth]{rotation_vs_pol.png}
	\caption{Rotation frequency vs component phase difference for differently sized dimers. The solid lines represent the rotation rate experienced while the dimer is in its standard orientation, whereas the solid points are for the case where the orientation is inverted. Laser power $= 100\ mW$}
\end{figure}

A possible explanation of this phenomena was devised by by \cite{Yevick2017}, 
who found that highly focused Gaussian beams could produce second 
order effects in the Rayleigh regime resulting in a photo-kinetic 
force that results in orbital motion about the beam's central axis. 
This effect is rather minimal for single sphere's, resulting in a 
orbital frequency on the order of $10^{-1}\,{\rm Hz}$, with an 
order of magnitude difference when trapping aggregates of spheres. 
They computed the circulation rate by computing the time-average 
probability flux; however, when extended to the Mie regime we 
see a completely different behaviour, instead experiencing an 
optical torque about their long axis.S This rotation was first 
noted by Vigilante and co-workers who only considered this
behaviour for a symmetric dimer \cite{Vigilante2020}; we run number of
simulations for differently sized dimers in a circularly polarised
trap and looked at the rotation rate.  We found that not only is the
rotation rate dependent on the size of the dimer, but also on its
orientation and therefore their axial position.
\begin{figure}[h!]
  \centering
  \includegraphics[width=\linewidth]{rotation_rate_vs_size.png}
  \caption{Rotation rate plotted against dimer size ratio for a variety of different simulation scenarios. The red line is for the case where the larger sphere is above the smaller sphere. The blue line is the inverted case, while the initial position is above the focus of the trap. And lastly the green line is again for the inverted case, but when the dimer's initial position is below the focus of the trap.}
\end{figure}

It is difficult to see from the graph, but the rotation rate never
truly goes down to zero, reaching a minimum of $2\,{\rm Hz}$, which would
imply that a second sphere of radius $200\,{\rm nm}$ is enough to
induce rotational motion. We used \textit{mstm} to look at the stokes
parameters from the scattered field from a simple plane wave incident
on our dimer, the proportion of circularly polarised light is minimal
compared to the proportion of plane polarised light, which indicates
that this rotational motion is not due to any inhomogeneity in the
dimer that might impart angular momentum to the scattered beam - as
compared to a anisotropic scatterer like vaterite.

These results are somewhat contrary to other work with silica dimers
\cite{Ahn2018, Debuysschere2023,Reimann2018}; previous experiments
have trapped the dimer in an orientation perpendicular to the beam
propagation direction.  The rotational motion is induced due to the
asymmetric geometry creating an unbalanced polarisation susceptibility
along its long axis as compared to its short axis; therefore its long
axis is aligned with the polarisation vector and can rotate
freely\cite{Ahn2018}.  This however cannot be the case with our
simulations as the dimer rotates about its long axis, meaning there
cannot be an asymmetric axis to align with the beam's polarisation
vector. Furthermore, we see a non-linear increase in the rotational
speed of our dimers with size, the drag torque from the surrounding
fluid is $\propto r^3$ so the expectation is that the rotation
frequency should fall off with increasing size.  This indicates that
the rotational motion is due to the shape asymmetry of the dimer and
not solely due to the beam's angular momentum.  Measurement of this
photo-kinetic force is difficult to achieve due to the fact that
previous analysis was conducted in the Rayleigh regime, where the
polarizability of our dimer can be approximated as:
\begin{align}
  \bold{p}({\bf r},t)
  =
  \alpha_x E_x({\bf r},t)\hat{\bf e}_x
  + \alpha_yE_y({\bf r},t)\hat{\bf e}_y
  + \alpha_zE_z({\bf r},t)\hat{\bf e}_z
\end{align}

where the polarizability is given as a 3D vector for the three
principle Cartesian directions.  In order to measure the magnitude of
second order contributions we would need to construct a dipole array
that fully captures the scattering of a dimer. Measuring the optical torque 
makes it clear that the polarizability is a contributing factor to this optical 
rotation phenomena. Rotating a symmetric dimer in the $x-z$ plane reveals 
that while the dimer can be rotated in an orientation perpendicular 
to the beam rotational torque is maximised when rotated while aligned with 
the optical axis.
\begin{SCfigure}
	\includegraphics[width=0.65\linewidth,height= 15cm]{torque_different_polarisations.png}
	\caption{Optical torque against polar angle $\theta$ about the three primary axis (top: torque about the x-axis; middle: torque about the y-axis; bottom: torque about the z-axis) on a symmetric dimer in linear, elliptical, and circular polarisation beams. Diagram to the right is for visual clarity about the direction of $\theta$.\vspace{4.5cm}}
\end{SCfigure}
\newpage

@@

As a benchmark we start by considering a single sphere within 
an optical trap. After a 3 second trajectory (the typical time
necessary to collect a power spectrum) the sphere's power 
spectra was recorded and a fitted to eq.~\ref{eq:alaised_lorentzian}.
\begin{figure}[h]
	\label{fig:psd_sphere}
	\centering
	\includegraphics[width=\linewidth]{PSD_sphere.png}
	\caption{Recorded power spectra fitted to eq.~\ref{eq:alaised_lorentzian}, scattered points represents the blocked data ($n_b=100$). Corner frequency for the 
	Lorentzian curves are reported in the legend.}
\end{figure}

@@

Where the ellipticity of the beam is given by 
$e = (1-\kappa_y/\kappa_x)^{0.5}$ and is a measure of the symmetry of 
the beam wavefront. Its clear from these initial results that the 
QPD is more sensitive to changes along the y-axis than the x-axis 
when compared to the direct \textit{ott} calculations. Typically,
even an industrial Gaussian beam will produce an elliptical diffraction
limit spot when heavily focused; in their tutorial for optimizing 
the PSD analysis, Berg and Sorensen reported a ellipticity of
around 15 \% after a total calibration time of 81 seconds 
\cite{BergSoerensen2004}. The reason for this discrepancy
can be explained partly by the fact that our estimation of the 
trap geometry via \textit{ott} is based on the force-displacement
curve while the sphere is moving in only one direction, whereas the
QPD is estimating the trap geometry by extrapolating from far field 
scattering signals. We now consider a symmetric dimer in identical 
simulative conditions.

@@

Now we see that the \textit{ott} predicts a more elliptical 
trap compared to the QPD model which says the trap is far
more symmetrical while trapping a symmetric dimer. A potential 
reason that \textit{ott} no longer expects a circular trap 
could be due to how it computes the beam shape coefficients; 
by point matching in the far field before the focus means a 
loss in accuracy for objects that trap above the focus. 
The change in the QPD estimation can be partially explained 
by the fact that rotational effects are not accounted for in 
the Lorentzian power spectra, only translational motion. 
Typically, rotational motion is only ever detected when it 
is periodic (take for example Fig.~\ref{fig:vaterite}), when 
the motion is stochastic the entire power spectra is effected 
making it near impossible to separate the translational and 
rotational contributions from a single power spectra.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
Considering the simplicity of a scatterer such as a dimer,
one would assume that the dynamics of such an object would be
relatively easy to predict. Simulations of dimers in the Mie regime
show that not only do they have multiple positions and orientations 
in which they can be trapped but also that their interaction
with circularly polarised light is heavily dependent on the axial 
position and trapping orientation. Dimer's have the potential to be used
as adaptive micro-rotors, being simple to synthesise and can be made 
out of any material of choice, but in order for these particles to be
used as such one needs a means of characterising the optical torque
applied. While estimations can be made in the Rayleigh regime due to 
the dimer being treated as point dipole, Mie regime micro rotors require 
an in-depth theoretical description of the mechanism that is creating 
this optical torque.

### 2024-07-11 Latex_files/Thesis/chapters/chapter 5/main.tex
updates

\chapter{Detection and Characterisation of rotational spherical aggregate rotational dynamics}
\section{Simulative QPD}
A QPD is simply a measure of the total electric field incident on a photo diode, in order to accurately simulate a QPD response careful consideration of how the Electromagnetic fields are defined is required.

\subsection{Incident beam}
\label{sec:scattering}
The incident beam is simple enough to define given our set up parameters, for the sake of simplicity we assume that our beam is a Laguerre-Gaussian beam of mode $[0.0, 0.0]$ (which is simply a pure Gaussian beam). *Ott* uses a point matching approach to approximate the beam shape coefficients of the incident field by fitting it to the far field estimate, the beam is of the form:

@@

\begin{figure}[h]
	\label{fig:Rohrbach}
	\begin{subfigure}{0.475 \linewidth}
		\subcaption{}
		\includegraphics[width=\linewidth]{QPD_axial_tests.png}
	\end{subfigure}
	\begin{subfigure}{0.475 \linewidth}
		\subcaption{}
		\includegraphics[width=\linewidth]{QPD_lat_tests.png}
	\end{subfigure}
	\caption{Comparison between QPD response signal versus work conducted by Rohrbach, single sphere ($r = 150\ nm$, $n=1.57$) is scanned by a $1064\ nm$ laser and the QPD signal recorded. Solid lines represent the signal produced by QPD using \textit{ott} and points represent the signal response collected from [].}
\end{figure}
Since we are only interested in the dynamics of spherical aggregates upon reaching equilibrium we do not need to be concerned about the deviation from Rohrbach's results so long as the particle's displacement does not exceed the linear region at the origin. The axial response curve is slightly more involved, requiring that the condenser lens numerical aperture is adjusted until a harmonic response curve is achieved \cite{Friedrich2012}.

>>>>

\chapter{Detection and Characterisation of rotational spherical aggregate rotational dynamics}
\label{chapter:simulated_detection}
\section{Simulative QPD}
A QPD is simply a measure of the total electric field incident on a photo diode, in order to accurately simulate a QPD response careful consideration of how the Electromagnetic fields are defined is required.

\subsection{Incident beam}
\label{sec:fibre_scattering}
The incident beam is simple enough to define given our set up parameters, for the sake of simplicity we assume that our beam is a Laguerre-Gaussian beam of mode $[0.0, 0.0]$ (which is simply a pure Gaussian beam). *Ott* uses a point matching approach to approximate the beam shape coefficients of the incident field by fitting it to the far field estimate, the beam is of the form:

@@

Since we are only interested in the dynamics of spherical aggregates upon reaching equilibrium we do not need to be concerned about the deviation from Rohrbach's results so long as the particle's displacement does not exceed the linear region at the origin. The axial response curve is slightly more involved, requiring that the condenser lens numerical aperture is adjusted until a harmonic response curve is achieved \cite{Friedrich2012}.
